---
title: "All Queens Data"
author: "Michael Weisner"
date: "3/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning=FALSE)
library(tinytex)
library(kableExtra)
library(qwraps2)
library(stringr)
library(jsonlite)
library(httr)
library(data.table)
library(lubridate)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(ggthemes)
options(qwraps2_markup = "markdown")
```

### Basic API Query
```{r, eval=FALSE}
test <- GET(paste0("https://aqs.epa.gov/data/api/sampleData/bySite?email=",EPA_EMAIL,"&key=",EPA_KEY,"&param=88502&bdate=20070101&edate=20070131&state=36&county=081&site=0124"))

test_content <- content(test)
test_data <- rbindlist(test_content$Data, fill = TRUE)
```

### PM2.5 Hourly Values


```{r}
# API Parameters
EPA_EMAIL <- Sys.getenv('EPA_EMAIL')
EPA_KEY <- Sys.getenv('EPA_KEY')
base_url <- "https://aqs.epa.gov/data/api/sampleData/bySite"

# 2006 Data
  args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20061201,
               edate=20061231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
  #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2006_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2006_df, "data/air_data/hourly/pm2.5/pm2.5_2006_hr_QUEENS.csv")

# 2007 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20070101,
               edate=20071231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2007_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2007_df, "data/air_data/hourly/pm2.5/pm2.5_2007_hr_QUEENS.csv")

# 2008 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20080101,
               edate=20081231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2008_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2008_df, "data/air_data/hourly/pm2.5/pm2.5_2008_hr_QUEENS.csv")

# 2009 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20090101,
               edate=20091231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2009_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2009_df, "data/air_data/hourly/pm2.5/pm2.5_2009_hr_QUEENS.csv")

# 2010 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20100101,
               edate=20101231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2010_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2010_df, "data/air_data/hourly/pm2.5/pm2.5_2010_hr_QUEENS.csv")

# 2011 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20110101,
               edate=20111231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2011_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2011_df, "data/air_data/hourly/pm2.5/pm2.5_2011_hr_QUEENS.csv")

# 2012 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20120101,
               edate=20121231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2012_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2012_df, "data/air_data/hourly/pm2.5/pm2.5_2012_hr_QUEENS.csv")

# 2013 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20130101,
               edate=20131231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2013_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2013_df, "data/air_data/hourly/pm2.5/pm2.5_2013_hr_QUEENS.csv")

# 2014 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20140101,
               edate=20141231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2014_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2014_df, "data/air_data/hourly/pm2.5/pm2.5_2014_hr_QUEENS.csv")

# 2015 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20150101,
               edate=20151231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2015_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2015_df, "data/air_data/hourly/pm2.5/pm2.5_2015_hr_QUEENS.csv")

# 2016 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20160101,
               edate=20161231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2016_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2016_df, "data/air_data/hourly/pm2.5/pm2.5_2016_hr_QUEENS.csv")

# 2017 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20170101,
               edate=20171231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2017_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2017_df, "data/air_data/hourly/pm2.5/pm2.5_2017_hr_QUEENS.csv")

# 2018 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20180101,
               edate=20181231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2018_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2018_df, "data/air_data/hourly/pm2.5/pm2.5_2018_hr_QUEENS.csv")

# 2019 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=88502,
               bdate=20190101,
               edate=20191231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

pm2.5_2019_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = pm2.5_2019_df, "data/air_data/hourly/pm2.5/pm2.5_2019_hr_QUEENS.csv")

# Full Data

pm2.5_2006_2019_df <- do.call("rbind", list(pm2.5_2006_df, pm2.5_2007_df, pm2.5_2008_df, pm2.5_2009_df, pm2.5_2010_df, pm2.5_2011_df, pm2.5_2012_df, pm2.5_2013_df, pm2.5_2014_df, pm2.5_2015_df, pm2.5_2016_df, pm2.5_2017_df, pm2.5_2018_df, pm2.5_2019_df))

pm2.5_2006_2019_df$date_time_local <- ymd_hm(paste(pm2.5_2006_2019_df$date_local, pm2.5_2006_2019_df$time_local), tz="EST")

pm2.5_2006_2019_df$date_time_gmt <- ymd_hm(paste(pm2.5_2006_2019_df$date_gmt, pm2.5_2006_2019_df$time_gmt), tz = "GMT")

pm2.5_2006_2019_df$date_time_gmt2 <- with_tz(pm2.5_2006_2019_df$date_time_local, tzone= "Europe/Athens") # This is Athens Time and is GMT+2

pm2.5_2006_2019_df$date_time_gmt2_value <- paste(pm2.5_2006_2019_df$date_time_gmt2) # backup
```

#### Create Adjusted PM2.5 Date 

The closing value for a day is reported at 4PM, so we adjust the PM2.5 average for a day to start the day before at 4PM and end the day of at 4PM. We can do this by adjusting the date to GMT + 2 and then removing the timestamp.

```{r}
pm2.5_2006_2019_df$snp_close_adjusted_date <- NA

# for(i in 1:nrow(pm2.5_2006_2019_df)) {
# pm2.5_2006_2019_df$snp_close_adjusted_date[i] <- paste(date(pm2.5_2006_2019_df$date_time_gmt2[i]))
# }

pm2.5_2006_2019_df$snp_close_adjusted_date <- paste(date(pm2.5_2006_2019_df$date_time_gmt2_value))

write_csv(x = pm2.5_2006_2019_df, "data/air_data/hourly/pm2.5/pm2.5_2006_2019_df_QUEENS.csv")
```

#### Data Check
```{r}
datacheck <- read_csv("data/air_data/hourly/pm2.5/pm2.5_2006_2019_df_QUEENS.csv")
```

```{r}

pm2.5_2006_2019_df <- read_csv("data/air_data/hourly/pm2.5/pm2.5_2006_2019_df_QUEENS.csv")

full_dates <- seq(as.Date("2006-12-21"), as.Date("2020-01-01"), by="days")
full_dates <- as.data.frame(full_dates)
colnames(full_dates)  <- "snp_close_adjusted_date"

full_dates <- left_join(full_dates, pm2.5_2006_2019_df)

#full_dates <- full_dates[-c(1:15),]

sum(is.na(full_dates$sample_measurement))
```

Between 2006-12-21 and 2020-01-01 I'm missing 4277 hourly measurements of pm2.5.

### Ozone Hourly Values

Daily mean measures of 1-hour ozone

For reference, the current national air quality standard for ozone is 0.08 parts per million (ppm), or 80 parts per billion (ppb), averaged over 8 hours. (NASA, 2003)
AQI code is 44201.


```{r}
EPA_EMAIL <- Sys.getenv('EPA_EMAIL')
EPA_KEY <- Sys.getenv('EPA_KEY')
base_url <- "https://aqs.epa.gov/data/api/sampleData/bySite"

# 2006 Data
  args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20061220,
               edate=20061231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
  #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2006_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2006_df, "data/air_data/hourly/ozone/ozone_2006_hr_QUEENS.csv")

# 2007 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20070101,
               edate=20071231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2007_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2007_df, "data/air_data/hourly/ozone/ozone_2007_hr_QUEENS.csv")

# 2008 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20080101,
               edate=20081231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2008_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2008_df, "data/air_data/hourly/ozone/ozone_2008_hr_QUEENS.csv")

# 2009 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20090101,
               edate=20091231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2009_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2009_df, "data/air_data/hourly/ozone/ozone_2009_hr_QUEENS.csv")

# 2010 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20100101,
               edate=20101231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2010_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2010_df, "data/air_data/hourly/ozone/ozone_2010_hr_QUEENS.csv")

# 2011 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20110101,
               edate=20111231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2011_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2011_df, "data/air_data/hourly/ozone/ozone_2011_hr_QUEENS.csv")

# 2012 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20120101,
               edate=20121231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2012_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2012_df, "data/air_data/hourly/ozone/ozone_2012_hr_QUEENS.csv")

# 2013 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20130101,
               edate=20131231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2013_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2013_df, "data/air_data/hourly/ozone/ozone_2013_hr_QUEENS.csv")

# 2014 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20140101,
               edate=20141231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2014_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2014_df, "data/air_data/hourly/ozone/ozone_2014_hr_QUEENS.csv")

# 2015 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20150101,
               edate=20151231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2015_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2015_df, "data/air_data/hourly/ozone/ozone_2015_hr_QUEENS.csv")

# 2016 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20160101,
               edate=20161231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2016_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2016_df, "data/air_data/hourly/ozone/ozone_2016_hr_QUEENS.csv")

# 2017 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20170101,
               edate=20171231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2017_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2017_df, "data/air_data/hourly/ozone/ozone_2017_hr_QUEENS.csv")

# 2018 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20180101,
               edate=20181231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2018_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2018_df, "data/air_data/hourly/ozone/ozone_2018_hr_QUEENS.csv")

# 2019 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=44201,
               bdate=20190101,
               edate=20191231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

ozone_2019_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = ozone_2019_df, "data/air_data/hourly/ozone/ozone_2019_hr_QUEENS.csv")

# Full Data

ozone_2006_2019_df <- do.call("rbind", list(ozone_2006_df, ozone_2007_df, ozone_2008_df, ozone_2009_df, ozone_2010_df, ozone_2011_df, ozone_2012_df, ozone_2013_df, ozone_2014_df, ozone_2015_df, ozone_2016_df, ozone_2017_df, ozone_2018_df, ozone_2019_df))

ozone_2006_2019_df$date_time_local <- ymd_hm(paste(ozone_2006_2019_df$date_local, ozone_2006_2019_df$time_local), tz="EST")

ozone_2006_2019_df$date_time_gmt <- ymd_hm(paste(ozone_2006_2019_df$date_gmt, ozone_2006_2019_df$time_gmt), tz = "GMT")

ozone_2006_2019_df$date_time_gmt2 <- with_tz(ozone_2006_2019_df$date_time_local, tzone= "Europe/Athens") # This is Athens Time and is GMT+2

ozone_2006_2019_df$date_time_gmt2_value <- paste(ozone_2006_2019_df$date_time_gmt2) # backup
```

#### Create Adjusted Ozone Date 

The closing value for a day is reported at 4PM, so we adjust the ozone average for a day to start the day before at 4PM and end the day of at 4PM. We can do this by adjusting the date to GMT + 2 and then removing the timestamp.

```{r, message=FALSE}
ozone_2006_2019_df$snp_close_adjusted_date <- NA

# for(i in 1:nrow(ozone_2006_2019_df)) {
# ozone_2006_2019_df$snp_close_adjusted_date[i] <- paste(date(ozone_2006_2019_df$date_time_gmt2[i]))
# }

ozone_2006_2019_df$snp_close_adjusted_date <- paste(date(ozone_2006_2019_df$date_time_gmt2_value))

write_csv(x = ozone_2006_2019_df, "data/air_data/hourly/ozone/ozone_2006_2019_df_QUEENS.csv")
```

```{r}
datacheck <- read_csv("data/air_data/hourly/ozone/ozone_2006_2019_df_QUEENS.csv")
```

#### Data Check
##### Missing
```{r}

ozone_2006_2019_df <- read_csv("data/air_data/hourly/ozone/ozone_2006_2019_df_QUEENS.csv")

full_dates <- seq(as.Date("2006-12-21"), as.Date("2020-01-01"), by="days")
full_dates <- as.data.frame(full_dates)
colnames(full_dates)  <- "snp_close_adjusted_date"

full_dates <- left_join(full_dates, ozone_2006_2019_df)

full_dates <- full_dates[-c(1:15),]

sum(is.na(full_dates$sample_measurement))
```

Between 2007-06-13 and 2019-12-01 we are missing 4362 hourly measurements. This makes a problem for calculating the sum and 8 hour averages.

### Carbon Monoxide Hourly Values
```{r}
EPA_EMAIL <- Sys.getenv('EPA_EMAIL')
EPA_KEY <- Sys.getenv('EPA_KEY')
base_url <- "https://aqs.epa.gov/data/api/sampleData/bySite"

# 2006 Data
  args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20061220,
               edate=20061231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
  #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2006_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2006_df, "data/air_data/hourly/CO/CO_2006_hr_QUEENS.csv")

# 2007 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20070101,
               edate=20071231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2007_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2007_df, "data/air_data/hourly/CO/CO_2007_hr_QUEENS.csv")

# 2008 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20080101,
               edate=20081231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2008_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2008_df, "data/air_data/hourly/CO/CO_2008_hr_QUEENS.csv")

# 2009 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20090101,
               edate=20091231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2009_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2009_df, "data/air_data/hourly/CO/CO_2009_hr_QUEENS.csv")

# 2010 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20100101,
               edate=20101231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2010_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2010_df, "data/air_data/hourly/CO/CO_2010_hr_QUEENS.csv")

# 2011 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20110101,
               edate=20111231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2011_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2011_df, "data/air_data/hourly/CO/CO_2011_hr_QUEENS.csv")

# 2012 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20120101,
               edate=20121231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2012_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2012_df, "data/air_data/hourly/CO/CO_2012_hr_QUEENS.csv")

# 2013 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20130101,
               edate=20131231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2013_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2013_df, "data/air_data/hourly/CO/CO_2013_hr_QUEENS.csv")

# 2014 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20140101,
               edate=20141231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2014_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2014_df, "data/air_data/hourly/CO/CO_2014_hr_QUEENS.csv")

# 2015 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20150101,
               edate=20151231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2015_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2015_df, "data/air_data/hourly/CO/CO_2015_hr_QUEENS.csv")

# 2016 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20160101,
               edate=20161231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2016_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2016_df, "data/air_data/hourly/CO/CO_2016_hr_QUEENS.csv")

# 2017 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20170101,
               edate=20171231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2017_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2017_df, "data/air_data/hourly/CO/CO_2017_hr_QUEENS.csv")

# 2018 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20180101,
               edate=20181231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2018_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2018_df, "data/air_data/hourly/CO/CO_2018_hr_QUEENS.csv")

# 2019 Data
args <- list(email=EPA_EMAIL, 
               key= EPA_KEY,
               param=42101,
               bdate=20190101,
               edate=20191231,
               state="36",
               county="081",
               site="0124")

  res <- GET(base_url, query = compact(args))
  # Check the result
 # #status_code(res)
  # Get the content and return it as a data.frame
  raw_query <- content(res)

CO_2019_df <- rbindlist(raw_query$Data, fill = TRUE)

write_csv(x = CO_2019_df, "data/air_data/hourly/CO/CO_2019_hr_QUEENS.csv")

# Full Data

CO_2006_2019_df <- do.call("rbind", list(CO_2006_df, CO_2007_df, CO_2008_df, CO_2009_df, CO_2010_df, CO_2011_df, CO_2012_df, CO_2013_df, CO_2014_df, CO_2015_df, CO_2016_df, CO_2017_df, CO_2018_df, CO_2019_df))

CO_2006_2019_df$date_time_local <- ymd_hm(paste(CO_2006_2019_df$date_local, CO_2006_2019_df$time_local), tz="EST")

CO_2006_2019_df$date_time_gmt <- ymd_hm(paste(CO_2006_2019_df$date_gmt, CO_2006_2019_df$time_gmt), tz = "GMT")

CO_2006_2019_df$date_time_gmt2 <- with_tz(CO_2006_2019_df$date_time_local, tzone= "Europe/Athens") # This is Athens Time and is GMT+2

CO_2006_2019_df$date_time_gmt2_value <- paste(CO_2006_2019_df$date_time_gmt2) # backup

```

#### Create Adjusted Carbon Monoxide Date 

The closing value for a day is reported at 4PM, so we adjust the CO average for a day to start the day before at 4PM and end the day of at 4PM. We can do this by adjusting the date to GMT + 2 and then removing the timestamp.

```{r, message=FALSE}
CO_2006_2019_df$snp_close_adjusted_date <- NA

# for(i in 1:nrow(CO_2006_2019_df)) {
# CO_2006_2019_df$snp_close_adjusted_date[i] <- paste(date(CO_2006_2019_df$date_time_gmt2[i]))
# }

CO_2006_2019_df$snp_close_adjusted_date <- paste(date(CO_2006_2019_df$date_time_gmt2_value))

write_csv(x = CO_2006_2019_df, "data/air_data/hourly/CO/CO_2006_2019_df_QUEENS.csv")
```

```{r}
datacheck <- read_csv("data/air_data/hourly/CO/CO_2006_2019_df_QUEENS.csv")
```

#### Checks
##### Missing
```{r}

CO_2006_2019_df <- read_csv("data/air_data/hourly/CO/CO_2006_2019_df_QUEENS.csv")

full_dates <- seq(as.Date("2006-12-21"), as.Date("2020-01-01"), by="days")
full_dates <- as.data.frame(full_dates)
colnames(full_dates)  <- "snp_close_adjusted_date"

full_dates <- left_join(full_dates, CO_2006_2019_df)

#full_dates <- full_dates[-c(1:15),]

sum(is.na(full_dates$sample_measurement))
```

Between 2008-07-10 and 2020-01-01 we are missing 3737 hourly measurements.



